### 2016-01-27 AcademicPaperSummaries/PaperSummaries.tex
Abrahms and half of Berrebi and Lackdawalla

\underline{Research question and research area} Does terrorist activity generate concessions for the violent group? He is writing as part of the ``does terrorism work'' debate. \\
\underline{Summary of argument and mechanism} Terrorism is unlikely to work politically because targeting civilians makes leaders unwilling, and politically unable, to make concessions.
\underline{Conceptualization of terrorism} Distinguishes between ``process'' and ``outcome'' goals, with the former being goals that help the group's operations and the latter being ``their stated political ends.'' Codes for campaigns that have killed at least one person from the targeted country for stated reason of announcing concessions. \\
\underline{Data \& methods} Codes 125 ``violent substate campaigns'' for ``every group ever designated'' as a Foreign Terror Organization. Dependent variable is whether the group's campaign resulted in government compliance.   \\
\underline{Findings} Terror campaigns are less effective than guerilla campaigns: groups that mainly attack military targets ``regularly'' achieve policy ends, while those that mainly attack civilians tend not to gain stated political goals.  \\
\underline{Notes} The question that I think that Abrahms elides is who the audiences for terrorism are: Abrahms assumes that the audience being influenced is always the government. But, terrorism in the context of many civil wars is less about the government than about compelling civilians and populations.  Issue is also about taking stated political goals at face value. \\

>>>>

\underline{Research question and research area} Does terrorist activity generate concessions for the violent group? He is writing as part of the ``does terrorism work'' debate. \\
\underline{Summary of argument and mechanism} Terrorism is unlikely to work politically because targeting civilians makes leaders unwilling, and politically unable, to make concessions. But, violence is an imperfect form of communication because target countries tend to assume that the group's demands are too extreme for the domestic political context.
\underline{Conceptualization of terrorism} Inclusion criteria are: designated by US, have killed at least one person from the targeted country for stated reason of announcing concessions; differentiates guerrilla from terror by whether the majority of deaths were military or civilian. Interesting that he distinguishes between ``process'' and ``outcome'' goals, with the former being goals that help the group's operations and the latter being ``their stated political ends.''  Assume that terrorism is a communication strategy that signals costs of non-compliance to a target country\\
\underline{Data \& methods} Codes 125 ``violent substate campaigns'' for ``every group ever designated'' as a Foreign Terror Organization. Dependent variable is whether the group's campaign resulted in government compliance; important independent variables are target selection, fighting capacity, stated political objective. Model is logit (model 1) and ordered logit (model 2). \\
\underline{Findings} Terror campaigns are less effective than guerilla campaigns: groups that mainly attack military targets ``regularly'' achieve policy ends, while those that mainly attack civilians tend not to gain stated political goals.  \\
\underline{Notes} The question that I think that Abrahms elides is who the audiences for terrorism are: Abrahms assumes that the audience being influenced is always the government. But, terrorism in the context of many civil wars is less about the government than about compelling civilians and populations.  Issue is also about taking stated political goals at face value. \\

\textbf{Berrebi, Claude and Esteban F. Klor. 2008. “Are Voters Sensitive to Terrorism?” American Political Science Review 102(3).}

\underline{Keywords:} empirical;

\underline{Research question and research area} Applying disaggregated data to underlying question of how terrorism influences voting patterns. \\
\underline{Definition of terrorism:} Terror attacks included if caused at least one non-combattant Israeli death.
\underline{Summary of argument and mechanism:} Terror attacks trigger residents of locality to alter their daily routine in response to perception of insecurity, (implied negative) influence on locality's economy and expected future income. These features antagonize the residents and makes them less supportive of concessions to Palestinian authority. Attacks in a locality also make the conflict more salient to residents of the locality [Note: not clear why this wouldn't be expected to apply to neighboring localities.]\\
\underline{Data \& methods:} Difference-in-difference. (Assumes that terror attacks are the only thing that differentiates patterns in voting across localities.) Dependent variable is vote share for political parties, for 1988, 1992, 1996, 199, and 2003. Terrorism measured via data on non-combattant Israeli fatalities from terror attacks.\\
\underline{Findings} Terrorism does cause polarization of the Israeli electorate, with a terror attack in a locality adding 1.35 percentage points to the locality's support for the political right.\\
\underline{Notes on related papers}\\
